Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-25 paper/ms.tex
update manuscript

@@

% TODO: SpType subtype?
\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$15
  million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Multi-color photometry requires eclipsing companions to have nearly
  identical color as TOI$\,$837, ruling out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios are limited
  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
  837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

Over the first one hundred million years of their lives, exoplanet
systems are expected to undergo major physical and dynamical changes.
For a typical Sun-like star, the protoplanetary disk disperses within
$\sim$3 million years (CITE IR + sub-mm results).  The planet
formation process presumably finishes within this time for gas giants
(CITE).  The rocky planet population will also be mostly evolved
within $\sim$3 million years (CITE), but may undergo significant
changes over the next $\sim$10-100 million years through giant
impacts.  The Moon, for instance, is thought to have formed when the
solar system was XX million years old through such an impact (CITE).

A number of other processes are thought to happen relatively quickly.
Physical changes in the sizes of planets are expected as they
contract, and as their atmospheres undergo photoevaporation
\citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
relative importance of these two processes is set by the planetary
mass, as well as the radiation environment.  Photoevaporation in
particular can be directly observed in {\it e.g.}, the He 10830\AA\
line (CITE, CITE, He-I or He-II?).  Dynamical changes are expected in
the semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change due to viscous coupling (CITE).
High-eccentricity migration processes including planet-planet
scattering (CITE), secular chaos (CITE), and Kozai-Lidov oscillations
(CITE) can also occur.  The circularization timescale is thought to be
such that for any giant planets that migrated early, their orbits
should circularize within 100 million years (CITE).

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
		{\it Top}: for bound companions,
		{\it Bottom}: for unassociated companions along the same line of
		sight.
		\label{fig:fpscenario}
	}
\end{figure*}

>>>>

%
% TODO:
% * Zhou or Quinn: what is the SpType? Add to abstract, tables, and
% text. G0V has been assumed.
%

@@

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$15
  million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Multi-color photometry requires eclipsing companions to have nearly
  identical color as TOI$\,$837, ruling out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios are limited
  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
  837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

Over the first 100 million years of their lives, exoplanet
systems are expected to undergo major physical and dynamical changes.
For a typical Sun-like star, the protoplanetary disk disperses within
roughly 1--10 million years
\citep{mamajek_initial_2009,dullemond_inner_2010,williams_protoplanetary_2011}.
Gas giants presumably finish accreting before the disk
disperses \citep{pollack_formation_1996}.  While rocky planets may
fully form within only a few million years
\citep{dauphas_hf-w-th_2011}, they can also undergo significant
changes over the next $\sim$10-100 million years through giant impacts
\citep[{\it
e.g.},][]{kleine_hf-w_2009,konig_earths_2011,raymond_terrestrial_2014}.
The Moon, for instance, may have formed from debris ejected during a
collision between the proto-Earth and a planetesimal
during Earth's first 100 million years
\citep{cameron_origin_1976,canup_origin_2001}.

A number of other processes are thought to shape young exoplanets.
Planets with gaseous envelopes are expected to shrink as they
contract, and as their atmospheres undergo photoevaporation
\citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017}.  The
relative importance of these two processes is set by the planetary
mass, as well as the radiation environment.  Photoevaporation in
particular can be directly observed in {\it e.g.}, the He 10830\AA\
line (CITE, CITE, He-I or He-II?).  Dynamical changes are expected in
the semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change due to viscous coupling (CITE).
High-eccentricity migration processes including planet-planet
scattering (CITE), secular chaos (CITE), and Kozai-Lidov oscillations
(CITE) can also occur.  The circularization timescale is thought to be
such that for any giant planets that migrated early, their orbits
should circularize within 100 million years (CITE).

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
		{\it Top}: for bound companions,
		{\it Bottom}: for unassociated companions along the same line of
		sight.
		Each constraint is described in Section~\ref{subsec:fp_constraints}.
		\label{fig:fpscenario}
	}
\end{figure*}
